---
title: "case study"
author: Pallavi Krishnamurthy
output: html_document
---
```{r set-up, include = FALSE}
library(tidyverse)
library(p8105.datasets)
library(leaflet)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## load airbnb package 

```{r}
data("nyc_airbnb")
```

## Brainstrom with this dataset 

*what is the best airbnb in staten island for <$100
*what price range is the most popular?
*what apartment features are related to the price?
*cheapest room type in each neighbourhood?
*hosts that have high ratings?

## Answer some questions

data cleaning 

```{r}
nyc_airbnb = 
  nyc_airbnb %>% 
  mutate(stars = review_scores_location / 2)
```

```{r}
 nyc_airbnb %>% 
  count(neighbourhood_group, room_type) %>% 
  pivot_wider(names_from = room_type, values_from = n)
```

```{r}
nyc_airbnb %>% 
  group_by(neighbourhood_group, room_type) %>% 
  summarize(mean_price = mean(price))
```

```{r}
nyc_airbnb %>% 
  filter(neighbourhood_group == "Manhattan") %>% 
  count(neighbourhood)

nyc_airbnb %>% 
  filter(
    price < 1000,
    neighbourhood_group == "Manhattan") %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
  ggplot(aes(x = neighbourhood, y = price)) +
  geom_boxplot() +
  coord_flip()
```

```{r}
nyc_airbnb %>% 
  sample_n(1000) %>% 
  ggplot(aes(x = lat, y = long, colour = price )) +
  geom_point()
```

## creat a leaflet map 

```{r}
pal <- colorNumeric("viridis", nyc_airbnb %>% pull(stars))

nyc_airbnb %>%
  sample_n(1000) %>% 
  leaflet() %>% 
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addCircleMarkers(~lat, ~long, radius = 1, color = ~pal(stars))
```

```{r}
pal <- colorNumeric("magma", nyc_airbnb %>% pull(stars))

nyc_airbnb %>% 
  drop_na(stars) %>% 
  sample_n(5000) %>% 
  leaflet() %>% 
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addCircleMarkers(~lat, ~long, radius = 1, color = ~pal(stars))
```

